\section{Conclusion}

\subsection{Current Achievement}

Our product, motion tuner is able to detect users? motion and play
corresponding music. The key part to achieve this goal is to analyze users?
acceleration and create music with corresponding volume and tone. First, it
transmits the information of uses? motion to terminals with the help of sensors.
Then it analyzes the raw data from sensors and filters acceleration by serial
protocol. Finally, it compares the acceleration with pre-set standards and
creates matched sound tracks with acceleration. To create final audio, it is
also able to mix different sound tracks to make music fluent. \\ 

Our product is designed for everyone living under pressure in
everyday life. It provides them with a new option for relaxation. Due to its
portability and low cost, it is convenient and inexpensive for users to dance
whenever and wherever. This advantage makes our product surpass traditional
dancing machines. Also, its sensitivity creates a nice platform for dance lovers
to practice by themselves and it always encourages users to explore new
movements with unique music on their own. Therefore, it can even act as an
instrument for dancers to give improvisation performances on stage. 

\input{part/expSharing}

\subsection{Future Development}

In the future, we are going to focus on improving user-friendly
design as well as bringing in more dancing modes. For user-friendly design, we
will beautify the interface of our app to make it more elegant and attractive.
Up to now we have two modes including power mode and story mode. In power mode,
users are encouraged to create their own music by dancing freely. In story mode,
users need to carry out a certain series of movements to the rhythm of played
music. According to our plan, there will be more than three modes with different
functions in our app to meet all the requirements of users. 

