\subsection{Experience Sharing}

In the progress, we have not only learned a lot about the port and Bluetooth,
but also knowledge about music. We used to read ports in the linux system. Some
functions cannot be used on the unity platform in Windows. We needed to deal
with a lot of changes in detail. Figuring out differences in principle between
systems is quite efficient. To convert motion to music, basic music knowledge is
needed to produce harmonic pieces. Our music is freestyle, which reminds me of
the freestyle in jazz. So we collected piano company pieces according to the
chord of the songs and changed the rhythm according to the style of the music.

Besides, we experienced great trouble with the quality of the original sources
when collecting them. We have learnt from this experience that finding a
fundamental  source is really important. Finally we choose GarageBand as the
source, which is published by Apple company. As we trying a lot of different
apps to get audio sources, we found that most useful apps are developed by
famous company. To some extent,  brands promises quality and some excellent has
its reason to be a paid app. We all have obligation to support legal paid copy. 

The most difficult part of the mobile part is the data transmission part.
Different from other sensors that use bluetooth to transfer data, in this
project, constant data stream is needed. In order to detect the immediate motion
of user's body, the updating frequency must be very quick up to 70 to 150 fps.
After getting the data, raw data cannot be applied at once. Some process such as
adding another burden to the CPU and memory must be accomplished. Hence, this
project give us a lesson about the selection of valid data and how to achieve
the balance between collecting and analyzing.  

For mobile part, the most valuable thing we learn from it is that we have
proceeded a full tech-product development process. First we look for what
current resources we can get. After comparing one with each other, we choose the
Unity engine as our platform. Then we learn the library function we can get to
get access to sensor data and to display graphical user interface and most
importantly, to play the generated music. 

The main difference between desktop and mobile terminal is that mobile phones
are highly integrated while we mainly build the electronics from scratch for
desktop parts. We fully take advantage of the mobile terminals. Once we have an
idea, such as a new mode or a new algorithm, we first test it on the mobile
phone. If the test result meets our goal, the new idea will be introduced to the
desktop terminal, keeping the two terminals synced. 

What’s more, we have to admit that the final functions are not the same as we
planned in our pitch. The great reason is that we do not focus on one single
mode, and the result is that we have several different modes but each mode does
not achieve very high level of accomplishment. So the project informs us the
importance of the planning and realizing. 

Finally, we have also improved a lot in technical communication. Initially, we
focus our most attention on designing our product and take little efforts on
presenting and communicating. Therefore, we fail to leave a deep impression on
the audience at progress presentation. After that, we gradually realize that it
is important to accomplish the actual product. However, how to convey our ideas
and concepts of the product to the audience is another topic, which is also of
great importance and well worth our paying full attention. With the help of
professors, we have a much better performance in the symposium. 