\section{Objectives}
\subsection{Difficulties}
\hspace*{2em}Since we divided Part 4\&5 into two parts, the mobile terminal part
and the PC terminal part, we will divide the Objective parts into these two
parts as well. They share many general objectives. 

\subsubsection{General Difficulties}
\begin{itemize}
\item Have enough audio source to generate variable music
\item Produce a harmonic music
\end{itemize}

\subsubsection{Mobile Terminal part}
\begin{itemize}
\item How to call the inner sensors in mobile phone
\item The calling of the speaker and the flashlight in mobile phone 
\end{itemize}

\subsubsection{PC Terminal part}
\begin{itemize}
\item Transform data from the sensor to the PC terminal
\end{itemize}



\subsection{Objectives of General Difficulties}

We want to have our own sound bank where we can take the certain audio sources
we need. Then basing on this bank, we can combine certain audio sources in a
harmonic way, in which audiences will enjoy this music. 
A standard will be set by an algorithm to determine which kind of music to
generate according to the corresponding motion. 

\subsection{Objectives of Mobile Terminal Part}

We want to use iPhone to detect our motion and then give out music. In other
words, by using iPhone, ideally, users don’t need any other sensors to take or
buy. In some other situations, users can use flash light to add to the fun of
his or her performance. 

\subsection{Objectives of PC Terminal Part}

We use a sensor to deter our motion. The data collected by the sensor will be
transformed to the PC terminal. It need an extra step than mobile phone
terminal. 


