\section{Tasks}

\subsection{General Tasks}

\subsubsection{Collecting and recording audio source}

In order to collect all kinds of audio source, we search the Internet to find
some short music with strong rhythm and can be looped. Since we have several
modes, different types of music may be useful. Moreover, we use the software
Garageband which consists of hundreds of audio source that we need. We record
each element we need in the software and then save them for future use. 

\subsubsection{Combine each audio source in a harmonic way}

Base on the theory of music such as the modal theory, we develop an algorithm
that can generate each audio source in a relatively harmonic way. Since it won’t
change the fact that if your motion is random and your music will also be
random, we can only try to reduce the effect of this problem. And further
development are still need in the future.  

\subsection{Mobile Terminal Tasks}

\subsubsection{Call the inner sensor in the iPhone}

The function of calling the sensor of iPhone has already been natively built.
We include a library and call a line of system function to get the sensor data,
which is in the form of 3-dimension vector.
The vector is preceessed later by separating its component in each direction.


\subsubsection{Call the speaker and flash light in the iPhone}

We use a group of Game Object which is designed to get access to cellphone's
hardware to call the speaker.
The object is very flexible, for we can change its volume, its source clip
easliy. 
We use Vufuria library (Widedly used in augmented reality field) to get easy
access to the flash light of iPhone.

\subsection{PC Terminal Tasks}

\subsubsection{Learn to transfer data from the sensor to the computer by
  bluetooth} 

First we need to learn the C\# language, which is used on the Unity platform.
Then search for information of serial port communication under the background of
C\#. 

